### 2015-01-09 fundamentals/intro.tex
intro

As nuclear power expands both domestically and internationally, nuclear fuel cycle
performance analysis on technical, economic, political, and environmental axes increases 
in importance. Appropriate nuclear fuel cycle analysis requires calculation of myriad physical, nuclear, 
chemical, industrial, and political phenomena. Nuclear fuel cycle simulators 
therefore couple complex systems such as nuclear process physics, 
facility deployment, and material routing. However, most nuclear fuel cycle 
simulators have not incorporated modern insights from simulation science and 
software architecture that can enable more efficient, accurate, robust, and 
validated analysis.

>>>>

As nuclear power expands both domestically and internationally, nuclear fuel
cycle performance analysis on technical, economic, political, and environmental
axes increases in importance. Appropriate nuclear fuel cycle analysis requires
calculation of myriad physical, nuclear, chemical, industrial, and political
phenomena. Nuclear fuel cycle simulators therefore couple complex systems such
as nuclear process physics, facility deployment, and material routing.
However, current fuel cycle simulators rely on closed platforms and inflexible
architectures which exhibit three main failure modes. First, they discourage
targeted contribution and collaboration among experts. Next, they hobble
efforts to directly comparison of modeling methodologies. Finally, they result
in over-specification, rendering most tools applicable to only a subset of
desired simulation fidelities, scales, and applications.  A next generation
fuel cycle simulator is needed which incorporates modern insights from
simulation science and software architecture to solve these problems. As a
bonus, many of these methods simultaneously enable more efficient, accurate,
robust, and validated analysis.
